\section{Analysis and Results}
\label{section:analysis}

\subsection{Scenarios}
- Benchmark: a lot of corners with minimal amount of obstacles\\
- Spiral: Also many corners, minimal distance\\
- SF: real world grid. Many obstacles, corners nearly always 90 degrees. Very predictable for algorithm\\
- Leuven: real world and irregular. Even more obstacles. Very unpredictable\\
\subsection{Theta* vs A*}
A* is faster, Theta* is easier to post-process. Theta* grid simplified.\\
Theta* needs line of sight checks. Slower than A*, but also prevents corner cutting in pre-path\\
Hierarchic indexed data structure for obstacles can greatly cut down on amount of LOS checks needed \\ IMPLEMENT?
\subsection{Genetic Algorithm}
Genetic algorithm takes extra time, bounding box includes more obstacles. cant use convex hull because potentially too restrictive\\
check GA parameters\\
\subsection{Curnercutting allowed vs not}
compare 2 corner cutting mitigations, show impact on time, path length\\
\subsection{Min/Max speed impact}
abs speed impact when not used (none?)\\
max speed impact\\
min speed impact\\
\subsection{Safety}
guaranteed by constraints, however:\\
no incentive to stay away from walls. Can increase vehicle size, but prevents occasionally getting closer for a short while.\\
\subsection{Stability and Performance}
-maxtime (max length of segment)\\
- approach margin: larger -> better approach, longer solve time\\
- tolerance: larger -> when corners are close, merge faster: more execution time\\
- position tolerance: larger -> smoother path, strays further from preprocessed path so needs to backtrack more often\\
- backtracking effect?\\
-can quickly recalculate based on measured state? IMPLEMENT WARM START EXPERIMENT?\\
\subsection{Other weaknesses}
waviness\\
bad approaches to corners\\
transitions between segments\\\\

eigen abs:\\
slack -> abs = val\\
-slack -> abs = -val\\\\

--> 2 vars voor abs\\\\

abs norm:\\
speed >= dot product[i]\\
slack[i] -> speed = dot product[i]\\\\

--> speed: num points / 4 vars\\\\

norm:\\
slack[i] and absslackx -> circle x\\
slack[i] and - absslackx -> - circle x\\\\

--> norm: geen extra vars   \\